---
title: "Alcohol vs Seat choice"
author: "Jarrod Harris"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
Based off the box plot the median people who sits in the back consumes more alcohol than the third quantile of people who sits in the front and those people who sits in the middle.   
 

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

The third quantile of the front is 2 and the third quantile of the numbers is the 3. The median pof the back is 4 so therefore the median in the back is higher than ythe third quantile of both the front and middle. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After running the inferential test it seem like the probability of people in the front and the middle are consuming the same amount of alcohol as the people in the back being at 0.00016. So there is a difference between the categories which is 3. 

```{r}
plot(TukeyHSD(model1))
```


## Conclusions


