---
title: "Alcohol vs Seat choice"
author: "Jarrod Harris"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
Based off the box plot the median people who sits in the back consumes more alcohol than the third quantile of people who sits in the front and those people who sits in the middle.   
 

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

The third quantile of the front is 2 and the third quantile of the numbers is the 3. The median pof the back is 4 so therefore the median in the back is higher than ythe third quantile of both the front and middle. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After running the inferential test it seem like the probability of people in the front and the middle are consuming the same amount of alcohol as the people in the back being at 0.00016. So there is a difference between the categories which is 3. 

```{r}
plot(TukeyHSD(model1))
```

When looking at the model above it shows how the middle compared to the back does not have 0 in their confidence interval. The same is true when you compare the front and the back to each other. It also indicate there is no statistical difference between the front and middle because the back is different from everybody else. 

## Conclusions

When going through the process with more than two variables there are more steps we have to go do which can delay the process. In this specific assignment we used the ggplot to create our box plot which showed us the median and amount of drinks that gets consumed in certain sections. Also we learned about the numerical summary to see the difference statistically and get differences in quantile. To get the probability of the same amount of drinks and consumption we ran the Inferential test and got a result of 0.000116. Using a comparison model the difference between the back compared to the front and middle is 3. 

